Karbowski model in 2-D

### 2020-01-16 paper/supplementary/supp.tex
Adds some notes on PNAS Reviewer 1's suggestion for an additional flux term.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Unimplemented ideas}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{PNAS Reviewer 1 suggestions}
\label{sec:comp15}

This mechanism was suggested by PNAS reviewer 1 who asked if we'd tried
anything similar to this as a way around requiring divisive
normalization.

This is similar to the ideas tried in Sections ~\ref{sec:comp2}
and \ref{sec:comp6}. The PNAS brief report submission Eq. 2 was:
%
\begin{equation}
\label{eq:comp15_eq0}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\mb{J}_i - \frac{\partial
c_i}{\partial t} + \chi
\end{equation}
%
Reviewer 1 suggested (where we might assume the equals sign in red was missed by typo):
%
\begin{equation}
\label{eq:comp15_eq1}
\chi \color{red}=\color{black} a_i \nabla \frac{1}{N-1} \sum_{j \ne i}^{N} a_j
\end{equation}
%
This isn't really sensible, because the gradient, which has direction, will be
positive on one side of a `hill of $a_{j\ne i}$' and negative on the other
side. Thus, $a$ would accumulate on one side and de-accumulate on the other,
rather than reducing all the way around the hill. However, if you took
the \emph{magnitude} of the gradient (along with a little rearranging, and the
incorporation of our parameter $\epsilon$) you get:
%
\begin{equation}
\label{eq:comp15_eq2}
\chi = - \frac{\epsilon_i  a_i}{N-1} \left\| \nabla  \sum_{j \ne i}^{N} a_j \right\|
\end{equation}
%
which may work, although it is unclear how this resolves the need for the
normalization that the reviewer (and we too) would like to avoid.

Although the reviewer prepended $\chi$ to this equation, they probably meant
adding to the flux term, which was the terminology they used. In that case, we
would have exactly Eq.~\ref{eq:J_NM_with_comp} and so yes, it was something we
tried, and I will try it again (Jan 2020) to refresh my memory of how it
worked.

\section{Unimplemented ideas}
